%
\begin{thebibliography}{9}



\bibitem{1} 
Mois\'es Na\'im. 
\textit{Ni Facebook, ni Twitter: son los fusiles}
https://elpais.com/diario/2011/02/27/internacional/1298761206\_850215.html , 2011.

\bibitem{2} 
Twitter. 
\textit{web page}
https://twitter.com/?lang=es , 2019.

\bibitem{3} 
CPI : Compa\~nia Peruana de Estudios de Mercado y Opini\'on P\'ublica s.a.c.. 
\textit{Market Report : Lima Digital}
http://cpi.pe/images/upload/paginaweb/archivo/26/MR\_Limadigital2018.pdf ,  pp3 , 01/2019.

\bibitem{4} 
SUNEDU 
\textit{Registro de trabajos de Investigaci\'on}
Bùsqueda : twitter analisis sentimientos.
http://renati.sunedu.gob.pe/simple-search , 2019.

\bibitem{5} 
INEI 
\textit{Una mirada a Lima Metropolitana}
https://www.inei.gob.pe/media/MenuRecursivo/publicaciones\_digitales/Est/Lib1168/libro.pdf , pp 9 , sept. 2014.


\bibitem{6} 
Taeho Jo-Text.
\textit{Mining Concepts, Implementation, and Big Data Challenge}. 
Springer, pp 3, 2018.
 
\bibitem{7} 
Bing Liu. 
\textit{Web Data Mining - Exploring Hyperlinks, Contents, and Usage Data. Second Edition}. 
Springer, pp 17, 2017.
 
\bibitem{8} 
Hassan, A. - Korashy, H.
\textit{"Sentiment analysis algorithms and applications: A survey",Ain Shams Engineering Journal}. 
Springer, vol. 5, no 4, pp 1093s–1113, 2017.
 
\bibitem{9} 
Francois Chollet.
\textit{Deep Learning with Python}. 
Manning Publications, pp 178-223, 2017.

\bibitem{10} 
Daniel S. Putler , Robert E. Krider
\textit{Customer and Business Analytics}. 
CRC Press, pp 19, 2012.

\bibitem{11} 
Abid Hussain , Ravi K. Vatrapu
\textit{Social Data Analytics Tool}. 
https://www.researchgate.net/publication/295257564\_Social\_Data\_Analytics\_Tool\_SODATO.
Conference Paper ,  2014.

\bibitem{12} 
Niels Buus Lassen, Ravi Vatrapu, Lisbeth la Cour, Rene Madsen, and Abid Hussain
\textit{Towards a Theory of Social Data: Predictive Analytics in the Era of Big Social Data}. 
https://research-api.cbs.dk/ws/portalfiles/portal/55458783/niels\_buss\_lassen\_towards\_a\_theory\_of\_social\_data\_publishersversion.pdf.
January 2018.

\bibitem{13} 
Zahra Iman, Scott Sanner, Mohamed Reda Bouadjenek, Lexing Xie
\textit{A Longitudinal Study of Topic Classification on Twitter}. 
https://www.aaai.org/ocs/index.php/ICWSM/ICWSM17/paper/download/15625/14852.
(ICWSM 2017

\bibitem{14} 
Niels Buus Lassen , Lisbeth la Cour, and Ravi Vatrapu
\textit{Predictive Analytics with Social Media Data}. 
The SAGE Handbook of Social Media Research Methods ,  pp 328 , 2016


\bibitem{15} 
Carrie Winterer
\textit{Thesis : Predicting Twitter TIme Series Using Generalized Linear Models}. 
Case Western Reserve University School of Graduates Studies - EEUU.
Department of Mathematics, Applied Mathematics and Statistics ,  August, 2018


\bibitem{16} 
Manuel Alejandro Rodr\'iguez Santana
\textit{Thesis : Predicción del éxito de los mensajes de Twitter}. 
Máster en Ingenier\'ia Inform\'atica, Facultad de Inform\'atica, Universidad Complutense de
Madrid ,  Junio, 2018

\bibitem{17} 
Xinsong Du , Jiang Bian and Mattia Prosperi
\textit{An Operational Deep Learning Pipeline for Classifying}. 
Dept. of Health Outcomes and Biomedical Informatics,
University of Florida, Gainesville, FL 32611, USA 2 Dept. of Epidemiology, University of Florida, Gainesville, FL 32611, USA








\end{thebibliography}